No need to know: astrophysics-agnostic gravitational wave cosmology

### 2024-03-11 src/tex/ms.tex
[showyourwork] overleaf sync

Additionally, we find spectral sirens will be most sensitive to $z=\variable{output/mostsensitivez.txt}$ at the end of \acf{O5}, .
This redshift is larger than the expected redshifts of detectable electromagnetic counterparts of binary neutron star mergers ~\citep{kiendrebogo_observing_2023}, meaning upgrades to current \ac{GW} detectors will allow the spectral siren method to probe $H(z)$ at otherwise unexplored distances.
Proposed next generation detectors such as Cosmic Explorer and Einstein Telescope will be sensitive to $z\sim40$.
Galaxy catalogs are anticipated to be complete to \result{$z=X$} at that time, and type 1a supernovae are expected to be observable to $z\simY$ \comment{cite Rubin papers?}, making the spectral siren method uniquely positioned to measure the expansion of the universe at high redshift.
While this sensitivity to high redshifts is a feature of the spectral siren method in general, non-parametric methods such as the one presented here will be imperative to avoid systematic biases as next-generation detectors provide additional data.

>>>>

Additionally, we find spectral sirens will be most sensitive to $z=\variable{output/mostsensitivez.txt}$ at the end of \acf{O5}, .
This redshift is larger than the expected redshifts of detectable electromagnetic counterparts of binary neutron star mergers ~\citep{kiendrebogo_observing_2023}, meaning upgrades to current \ac{GW} detectors will allow the spectral siren method to probe $H(z)$ at otherwise unexplored distances.
Proposed next generation detectors such as Cosmic Explorer and Einstein Telescope will be sensitive to $z\sim40$.
Galaxy catalogs are anticipated to be complete to \result{$z=X$} at that time, and type 1a supernovae are expected to be observable to $z\sim Y$ \comment{cite Rubin papers?}, making the spectral siren method uniquely positioned to measure the expansion of the universe at high redshift.
While this sensitivity to high redshifts is a feature of the spectral siren method in general, non-parametric methods such as the one presented here will be imperative to avoid systematic biases as next-generation detectors provide additional data.
